Final Project Part 3 Report

### 2024-12-05 final_paper/final_report.Rmd
Fixed commit issues

# Methods

```{r}
#| include: false
#| warning: false
#| message: false

@@

# Results {#sex-results}

@@

```{r}
#| include: false
#| warning: false
#| message: false

@@

```{r}
library(knitr)

# Model Performance Metrics
performance_metrics <- data.frame(
  Metric = c(
    "Multiple R^2 (Training Data)",
    "Adjusted R^2 (Training Data)",
    "Residual Standard Error (Training Data)",
    "RMSE (Cross-Validation)",
    "MAE (Cross-Validation)",
    "Cross-Validated R^2",
    "MSE (Test Data)",
    "R-squared (Test Data)"
  ),
  Value = c(
    0.9946,
    0.9937,
    0.01029,
    0.01110,
    0.00953,
    0.9933,
    2.621146e+12,
    -8648944050
  )
)

@@

# Ethics Discussion {#sex-ethics}

>>>>

\newpage 
# Methods

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Results {#sec-results}

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
# Model Performance Metrics
performance_metrics <- data.frame(
  Metric = c(
    "Multiple R^2 (Training Data)",
    "Adjusted R^2 (Training Data)",
    "Residual Standard Error (Training Data)",
    "RMSE (Cross-Validation)",
    "MAE (Cross-Validation)",
    "Cross-Validated R^2",
    "MSE (Test Data)",
    "R-squared (Test Data)"
  ),
  Value = c(
    0.9946,
    0.9937,
    0.01029,
    0.01110,
    0.00953,
    0.9933,
    2.621146e+12,
    -8648944050
  )
)

@@

# Ethics Discussion {#sec-ethics}
